---
title: "intro_to_healthiar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro_to_healthiar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Hi there!

This vignette will 1) tell you about the `healthiar`, 2) help you install the `healthiar` package, and 3) show you how to use `healthiar` with the help of examples.

*NOTE*: the development of `healthiar` is still ongoing. Any feedback regarding bugs, unclear documentation, ... is welcome and highly appreciated. Please provide feedback via a [GitHub issue](https://github.com/best-cost/best-cost_WPs/issues).

# About `healthiar`

blablabla

# How to install `healthiar`

## Initial installation

Prerequisite: access to the [BEST-COST GitHub repository](https://github.com/best-cost/best-cost_WPs) with your GitHub account

For initial installation follow the detailed steps in the [README](https://github.com/best-cost/best-cost_WPs?tab=readme-ov-file#readme). The main steps are:

1.  Generate a GitHub personal access token (PAT)
2.  Use your PAT to connect RStudio with your GitHub profile
3.  Install the newest version of `healhtiar` by running code below

```{r setup, eval=FALSE, include=TRUE}
credentials::set_github_pat() # Paste GitHub PAT if prompted

devtools::install_github(
  repo = "best-cost/best-cost_WPs",
  subdir = "/r_package/healthiar",
  ref = "HEAD", # By default "HEAD"; branch name to install package from  
  force = TRUE
)

library(healthiar)
```

## Updating `healthiar`

After the initial installation we recommend to regularly update `healthiar` by running the code provided in step 3 above.

# How to use `healthiar`

## Attribute health impacts to population-weighted mean exposure

```{r, eval=TRUE, include=TRUE}
getwd()
knitr::opts_knit$set(root.dir = getwd())
load("../testing/input/data/input_data_for_testing_Rpackage.RData")
print(airqplus_pm_copd$analysis_name)
```

```{r, eval=FALSE, include=TRUE}
bestcost_pm_copd <-
  healthiar::attribute_health(
    exp_central = airqplus_pm_copd$mean_concentration,
    cutoff_central = airqplus_pm_copd$cut_off_value,
    bhd_central = airqplus_pm_copd$incidents_per_100_000_per_year/1E5*airqplus_pm_copd$population_at_risk,
    rr_central = airqplus_pm_copd$relative_risk, 
    rr_lower = airqplus_pm_copd$relative_risk_lower,
    rr_upper = airqplus_pm_copd$relative_risk_upper,
    rr_increment = 10, 
    erf_shape = "log_linear", 
    info = paste0(airqplus_pm_copd$pollutant,"_", airqplus_pm_copd$evaluation_name))

```
