---
title: "Testing healthiar"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

------------------------------------------------------------------------

```{r prepare, include=FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(healthiar)
library(tibble)
library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(knitr)
library(readxl)
library(remotes)

## Avoid using pacman here, as it causes error in installation if it's not installed already
# library(pacman)
# pacman::p_load(healthiar, tibble, dplyr, purrr, tidyr, stringr, knitr, readxl)

options(knitr.kable.max_rows = 10)
set.seed(1)

```

## Hi there : )

This document will guide you step-by-step through the process of adding a test for a specific calculation pathway.

In case you encounter difficulties, you find something unclear or you see a way to improve the testing process, please let us know:

-   Preferably by opening a GitHub issue by going on this [link](https://github.com/best-cost/best-cost_WPs/issues) and clicking the green button that says *New issue* or

-   write us at [axel.luyten\@swisstph.ch](mailto:axel.luyten@swisstph.ch){.email} or [alberto.castrofernandez\@swisstph.ch](mailto:alberto.castrofernandez@swisstph.ch){.email}

Thank you in advance for your efforts! Together we can make healthiar more error proof and improve function and package documentation!

## Prerequisite: newest version of `healthiar` installed

If you haven't already, install the most recent version of the BEST-COST R package `healthiar`. If you get prompted to update packages that `healthiar` uses and/or relies on, we recommend to do so.

```{r install package, include=TRUE, echo=TRUE, eval=FALSE}
remotes::install_github(
  repo = "best-cost/best-cost_WPs", 
  subdir = "/r_package/healthiar", 
  ref = "HEAD", 
  build_vignettes = TRUE)
```

For more information on how to use the `healthiar` package (including several example cases of how to use the functions), please see the vignette `intro_to_healthiar`: you can access it (once you have the `healthiar` package installed) in RStudio by

-   running `browseVignettes("healthiar")` in the console and clicking on *HTML* on the page that pops up

-   going to the *Packages* tab in RStudio, and clicking on `healthiar`\>*User guides, package vignettes and other documentation*\>*HTML*

------------------------------------------------------------------------

# Example: Adding a test calculation

Below you will be guided step-by-step through the process of adding a test calculation. There are four main steps. They are, in order:

1.  Pick a pathway and look for comparison assessment

2.  Fill out the function template with the assessment input data

3.  IF POSSIBLE: Compare results of `healthiar` and your chosen assessment

4.  Upload the test

## 1. Pick a pathway and look for comparison assessment

You can either

-   Option A: first look for a comparison assessment & then select the corresponding pathway

-   Option B: first choose a pathway & then look for corresponding comparison assessment

    -   Recommended in case you have a specific assessment ready

Both options are valid. In the best case the pathway that you want to test is not yet covered / claimed by another WP4 partner. Please check this before you start creating your test case in the the Excel *overview_testing.xlsx*, which is located on Teams under [Documents\>WP4 PROGRAMMING\>testing_of_functions](https://ugentbe.sharepoint.com/:f:/r/teams/Group.PR202302461/Gedeelde%20documenten/WP4%20PROGRAMMING/testing_of_functions?csf=1&web=1&e=ByCQGk).

Note: it is okay to test a specific pathway more than once, but of course testing a new pathway adds the most value.

Of course, there are multiple possible sources of comparison assessments. These are, in order of decreasing preference:

1.  own assessment / calculations

2.  other studies / reports

3.  artificial intelligence, e.g. ChatGPT

4.  “fake” (but realistic) input data, to make sure calculation works (no error) and that results stay the same over timeFor picking a calculation pathway you can either

### Option A: Look for comparison assessment & select corresponding pathway

Example: you have done an assessment in the past and you claim the pathway in the Excel *overview_testing.xlsx* and get started with Step 2 right away.

### Option B: Choose a pathway & look for corresponding comparison assessment

Example: you have a look at the calculation pathways in the Excel *overview_testing.xlsx* and you select the following pathway:

-   Relative risk

-   ERF shape: log-linear

-   Exposure: exposure distribution

-   No iteration

The `pathway_id` of this calculation pathway is: *\|pathway_rr\|erf_log_lin\|exp_single\|iteration_FALSE\|*.

You claim this pathway by filling in your institution abbreviation and your name in the corresponding columns.

Each calculation pathway has a unique *pathway_id* linked to it, which contain all the infos from the characterisation columns in a condensed way. These pathways are used internally to keep track of the testing progress, and to find specific pathways quickly.

You ask around and find out that a colleague of you just recently did an assessment that matches your selected pathway. She digs up the assessment and sends you both the input data and the results. You get set to add a test. In this case, the assessment details are saved in a .xlsx file (Excel file).

Please see the start of Step 1 for alternative sources of comparison assessments.

### Detailed pathway characterizations

The Excel *overview_testing.xlsx*, which is located on Teams under [Documents\>WP4 PROGRAMMING\>testing_of_functions](https://ugentbe.sharepoint.com/:f:/r/teams/Group.PR202302461/Gedeelde%20documenten/WP4%20PROGRAMMING/testing_of_functions?csf=1&web=1&e=ByCQGk), contains an overview of the most relevant (= core) pathways that are available to users of *healthiar* functions. There are different sheets. In the first sheet is the overview of the core relative risk pathways. The columns might seem a bit cryptic at first glance, but bear with me:

-   *erf* contains the exposure-response function shape

    -   lin_lin = linear-linear ERF shape
    -   log_lin = log-linear ERF shape
    -   function = case where the ERF is defined by multiple points (x and y coordinates), e.g. the MR-BRT curves from GBD
    -   formula = case where ERF is a formula of the type a * x + b * x^2 ...

-   *exp* specifies the type of exposure input data

    -   single = single exposure input value, e.g. yearly average population-weighted PM2.5 exposure
    -   dist = exposure distribution, e.g. 5 different exposure categories (\~ exposure ranges) with the information how many people are exposed to each of the 5 exposure range

-   *iteration* specifies whether the assessment is done for more than one geo unit (e.g. municipality, region, province, ...)

    -   if yes –\> TRUE
    -   if no –\> FALSE

Similarly, pathways are also defined (with some different columns) for cost-benefit analysis, monetization, and the other pathway groups.

Detailed explanations of these other pathway IDs (like the bullet points above for the RR pathways) are found below at the start of each pathway groups' template.

## 2. Fill out the function template with the assessment input data

You create a new R script (`.R` file) or RMarkdown (`.Rmd` file) for your test (please create one file for each test, if possible).

You select the appropriate template that Swiss TPH provided.

Several testing templates can be found below in the section [Testing templates].

Below you find two variants of an example function template for a relative risk pathway

-   Option A: Basic function template

-   Option B: Extended function template (preferred)

Each template in the section [Testing templates] is available in both the basic and extended version.

### Option A: Basic function template

The basic template consists of the following elements

-   pathway ID (of the specific pathway you want to test)

-   if applicable: some code to load in input data

-   an `attribute_...` function call (in this case `attribute_health`) with (some of the) the function arguments needed for the assessment listed

-   an info block where we'd like you to enter

    -   result(s) (of the comparison assessment you selected)

    -   your name and institution abbreviation

    -   a short description of the comparison assessment you selected

    -   info about the input data you used

If you have just started your R journey, feel free to use the basic function template!

```{r basic template, include=TRUE, echo=TRUE, eval=FALSE}
## Pathway ID: copy here the pathway ID

## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

## healthiar FUNCTION CALL
results <- healthiar::attribute_health(
  erf_shape = ,
  rr_central = ,
  rr_increment = ,
  exp_central = ,
  prop_pop_exp = ,
  cutoff_central = ,
  bhd_central = ,
  geo_id_disaggregated = ,
  geo_id_aggregated =  
)

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Option B: Extended function template (preferred)

The extended function template contains the same elements as the basic function template plus it enables an automatic comparison of the `attribute_...` results and of the comparison assessment results. It contains the following additional elements

-   a `testthat::test_that` call, which contains the test name (1st argument) and contains the actual test (2nd argument), which is encapsulated by `{ ... }` and consists of

    -   a `testthat::expect_equal` call, which in turn encapsulates two main arguments

        1.  `object`: here you enter the `healthiar` function call. The output of the call will be compared with the second argument

        2.  `expected`: here you enter the result(s) of the comparison assessment

The extended function template is used in the automatic testing of the R package (for more info see [this chapter](https://r-pkgs.org/testing-basics.html) in Hadley Wickham's R packages book).

```{r extended template, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct <pathway_id>", {
  
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

testthat::expect_equal(
  ## healthiar FUNCTION CALL
  object =
    healthiar::attribute_health(
      erf_shape = ,
      rr_central = ,
      rr_increment = ,
      exp_central = ,
      prop_pop_exp = ,
      cutoff_central = ,
      bhd_central = ,
      geo_id_disaggregated = ,
      geo_id_aggregated = 
    )$health_main$impact_rounded,
  ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
  expected =
    c( )
)
})

## ASSESSOR: 
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

Please refer to the *intro_to_healthiar* vignette for guidance on how to extract main / detailed results of an attribute output.

### Add test details

In this example, we'll start by entering the `pathway_id` (which is found in the *overview_testing* Excel located in [this Teams folder](https://ugentbe.sharepoint.com/:f:/r/teams/Group.PR202302461/Gedeelde%20documenten/WP4%20PROGRAMMING/testing_of_functions?csf=1&web=1&e=ByCQGk)) to the function template.

In this example the `pathway_id` is *\|pathway_rr\|erf_log_lin\|exp_single\|iteration_FALSE\|*

In case of the basic template you add the `pathway_id` to the top of it:

```{r add test name basic, include=TRUE, echo=TRUE, eval=FALSE}
## Pathway ID: 
## |pathway_rr|erf_log_lin|exp_single|iteration_FALSE|
```

In case of the extended template you add the first argument of the `testthat::test_that` call:

```{r add test name extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct |pathway_rr|erf_log_lin|exp_single|iteration_FALSE|", { ... })
```

Then we'll continue by adding other details (same for basic & extended template) that describe the comparison case in more detail:

```{r add test details, include=TRUE, echo=TRUE, eval=FALSE}
## ASSESSOR: 
## Axel Luyten, Swiss TPH
## ASSESSMENT DETAILS: 
## attribute DALYs from ischemic heart disease to road noise exposure
## INPUT DATA DETAILS: 
## noise exposure data from NIPH; cutoff based on exposure data; baseline DALYs from GBD; relative risk from WHO (2003)

```

In case your comparison assessment has a *DOI*, please add it.

### Enter input data

Then you fill out the rest of the template using the input data of your selected assessment. There are two options:

-   Option A: Enter the input data hard-coded

-   Option B: Enter the input data by loading the data first into RStudio and then access it e.g. using the `$` operator

Depending on the assessment, one of the two might be better suited. We will first look at option A, and then at option B.

The step of entering the input data is the same for the basic & extended templates.

If you don't have much R programming experience, it's easiest to create the test with hard-coded inputs.

In case you load the input data before calling the `healthiar` function, please also upload the input data to the Teams testing folder of your institute, alongside the code for the test.

For the sake of visibility in this section only the `attribute_...` function call will be shown.

#### Option A: Function call with hard-coded data

We can manually open the (Excel) file containing the assessment details, and then copy the relevant input data into the template.

To see the Excel file used in this example, run

`shell.exec(dirname(system.file("extdata", "example_road_noise_niph.xlsx", package = "healthiar")))`

which will open the folder containing the *.xlsx* file of the example assessment.

Here's the filled out template with hard-coded input data, i.e. raw numbers are fed to the function arguments and no external input data are loaded into RStudio.

```{r test with hard-coded inputs, include=TRUE, echo=TRUE, eval=FALSE}
## healthiar FUNCTION CALL
results <- healthiar::attribute_health(
  erf_shape = "log_linear",
  rr_central = 1.08,
  rr_increment = 10,
  exp_central = c(53.0, 57.5, 62.5, 67.5, 72.5, 77.5),
  prop_pop_exp = c(4268785, 387500, 286000, 191800, 72200, 7700),
  cutoff_central = 53,
  bhd_central = 85362.08,
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
)
```

#### Option B: Function call with pre-loaded data

Another option is to load all your necessary input data before calling the `attribute_...` function.

In case you select this approach, remember to also upload the input data to the Teams testing folder of your institute, alongside the code for the test.

```{r inspect excel file, eval=FALSE, include=FALSE, eval=FALSE}
# system.file("extdata", package = "healthiar") |> list.files()
# test <- readxl::read_xlsx(path = system.file("extdata", "example_road_noise_niph.xlsx", package = "healthiar"), sheet = "Relative_risk_IHD_WHO_2003a")
```

```{r test with loaded inputs, include=TRUE, echo=TRUE, eval=FALSE}
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
data_raw  <-  readxl::read_xlsx(
  path = system.file("extdata", "example_road_noise_niph.xlsx", package = "healthiar"),
  sheet = "Relative_risk_IHD_WHO_2003a")
data  <- data_raw |>
  dplyr::filter(!is.na(data_raw$exposure_mean))

## healthiar FUNCTION CALL
results <- healthiar::attribute_health(
  erf_shape = "log_linear",
  rr_central = 1.08,
  rr_increment = 10,
  exp_central = data$exposure_mean,
  prop_pop_exp = data$prop_exposed,
  cutoff_central = min(data$exposure_mean),
  bhd_central = data$gbd_daly[1],
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
) 
```

Note that in case of the extended template

-   the input data is loaded just before the `testthat::expect_equal`

-   the `attribute_...` function call is fed to the `object` argument of the `testthat::expect_equal` call

### Enter results of comparison assessment

Next you enter the results of the comparison assessment you selected.

In case of the basic function template, you add the results to the info block at the bottom of the template.

```{r add results basic}
## RESULT(S) COMPARISON ASSESSMENT:
## 1151 attributable DALYs
```

In case of the extended function template, the results are fed to the `expected` argument of the `testthat::expect_equal` call.

```{r add results extended, include=TRUE, echo=TRUE, eval=FALSE}
# [...]
  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object = ,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      data_raw |>
      dplyr::filter(exposure_category %in% "Total exposed")|>
      dplyr::select(daly)|>
      dplyr::pull() |>
      round()
)
# [...]
```

## 3. IF POSSIBLE: Compare results of healthiar and your chosen assessment

Now you'll check whether the results of the `healthiar` function and your chosen comparison assessment are the same. You can either

-   Option A: compare the results manually

-   Option B: compare the results automatically (preferred)

If the results are the same you indicate this by putting *TRUE* in the Excel column *results_the_same*.

However, in case there is a deviation between the `healthiar` output and the results from the comparison assessment, you would put *FALSE* in the Excel column *results_the_same.*

Please try to judge what could cause the difference and leave a comment in the Excel. If you're unsure what's the issue and can't fix it yourself, we can discuss it together and maybe another WP4 partner can help.

### Option A: Compare results manually

```{r compare results manually, include=TRUE, echo=TRUE, eval=TRUE}
## healthiar FUNCTION CALL
results <- healthiar::attribute_health(
  erf_shape = "log_linear",
  rr_central = 1.08,
  rr_increment = 10,
  exp_central = c(53.0, 57.5, 62.5, 67.5, 72.5, 77.5),
  pop_exp = c(4268785, 387500, 286000, 191800, 72200, 7700),
  cutoff_central = 53,
  bhd_central = 85362.08,
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
)

results$health_main$impact_rounded |> 
  print()

## RESULT(S) COMPARISON ASSESSMENT:
## 1151 attributable DALYs
```

In this case the results are the same!

Please refer to the *intro_to_healthiar* vignette for guidance on how to extract main / detailed results of an attribute output.

### Option B: Compare results automatically (preferred)

If you have advanced knowledge of R we are very grateful if you can compare the results automatically by running the `test_that` function.

```{r compare results automatically, include=TRUE, echo=TRUE, eval=TRUE}
testthat::test_that("results correct |pathway_rr|erf_log_lin|exp_single|iteration_FALSE|", {
  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::attribute_health(
        exp_central = c(53.0, 57.5, 62.5, 67.5, 72.5, 77.5),
        pop_exp = c(4268785, 387500, 286000, 191800, 72200, 7700),
        cutoff_central = 53,
        bhd_central = 85362.08,
        rr_central = 1.08,
        rr_increment = 10,
        erf_shape = "log_linear",
        geo_id_disaggregated = NULL,
        geo_id_aggregated = NULL
      )$health_main$impact_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c(1151)
  )
})
```

Yes, in this case they are the same (the function printed `Test passed`)

Please refer to the *intro_to_healthiar* vignette for guidance on how to extract main / detailed results of an attribute output.

## 4. Upload the test

Once you've completed the previous steps you can change the value in the column *finished* in the Excel *overview_testing* from *FALSE* to *TRUE* to indicate that you are done with the assessment.

Please check that your test file clear sufficiently documented, i.e. someone who sees your test file for the first time should be able to understand what calculation pathway you covered, which input data was used, which comparison assessment you used, ... it is worth to invest a bit of time here, as it will also help you when you see this file again some time from now!

Finally, you upload your test with the `pathway_id` as the file name to the [Teams folder WP4 PROGRAMMING\>testing_of_functions](https://ugentbe.sharepoint.com/:f:/r/teams/Group.PR202302461/Gedeelde%20documenten/WP4%20PROGRAMMING/testing_of_functions?csf=1&web=1&e=hT3jaK) to the folder of your institute.

Filled out basic template (with hard-coded input data):

```{r filled out template basic, include=TRUE, echo=TRUE, eval=TRUE}
## Pathway ID: |pathway_rr|erf_log_lin|exp_single|iteration_FALSE|

## healthiar FUNCTION CALL
healthiar::attribute_health(
  erf_shape = "log_linear",
  rr_central = 1.08,
  rr_increment = 10,
  exp_central = c(53.0, 57.5, 62.5, 67.5, 72.5, 77.5),
  pop_exp = c(4268785, 387500, 286000, 191800, 72200, 7700),
  cutoff_central = 53,
  bhd_central = 85362.08,
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
)$health_main$impact_rounded |> 
  print()

## RESULT(S) COMPARISON ASSESSMENT:
## 1151 attributable DALYs
## ASSESSOR: 
## Axel Luyten, Swiss TPH
## ASSESSMENT DETAILS: 
## attribute DALYs from ischemic heart disease to road noise exposure
## INPUT DATA DETAILS: 
## noise exposure data from NIPH; cutoff based on exposure data; baseline DALYs from GBD; relative risk from WHO (2003)
```

Please refer to the *intro_to_healthiar* vignette for guidance on how to extract main / detailed results of an attribute output.

Filled out extended template (with input data loaded into RStudio):

```{r filled out template extended, include=TRUE, echo=TRUE, eval=TRUE}
testthat::test_that("results correct |pathway_rr|erf_log_lin|exp_single|iteration_FALSE|", {

  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  data_raw  <-  readxl::read_xlsx(
    path = system.file("extdata", "example_road_noise_niph.xlsx", package = "healthiar"),
    sheet = "Relative_risk_IHD_WHO_2003a")
  data  <- data_raw |>
    dplyr::filter(!is.na(data_raw$exposure_mean))
  
  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::attribute_health(
        erf_shape = "log_linear",
        rr_central = 1.08,
        rr_increment = 10,
        exp_central = data$exposure_mean,
        pop_exp = data$population_exposed_total,
        cutoff_central = min(data$exposure_mean),
        bhd_central = data$gbd_daly[1],
        geo_id_disaggregated = NULL,
        geo_id_aggregated = NULL
        )$health_main$impact_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      data_raw |>
      dplyr::filter(exposure_category %in% "Total exposed")|>
      dplyr::select(daly)|>
      dplyr::pull() |>
      round()
  )
})

## ASSESSOR: 
## Axel Luyten, Swiss TPH
## ASSESSMENT DETAILS: 
## attribute DALYs from ischemic heart disease to road noise exposure
## INPUT DATA DETAILS: 
## noise exposure data from NIPH; cutoff based on exposure data; baseline DALYs from GBD; relative risk from WHO (2003)
```

Please refer to the *intro_to_healthiar* vignette for guidance on how to extract main / detailed results of an attribute output.

------------------------------------------------------------------------

# Testing templates

For more information on how to use the `healthiar` package (including several example cases of how to use its functions), please see the vignette `intro_to_healthiar` (refer to section [Prerequisite: newest version of `healthiar` installed] for how to access it). For more information on a specific function, you can call `?healthiar::<function_name>` (e.g. `?healthiar::attribute_health`), which will open the function documentation. An alternative way to open the function documentation is to go to the *Packages* tab in RStudio, scroll down to & click on *healthiar*, and scroll down and click on the function you are interested in.

## Relative risk pathways

Depending on your calculation pathway you will have to replace some of the `NULL` values in the template.

### Explanation of pathway ID

The pathway ID for relative risk pathways contain the following elements:

-   *erf* contains the exposure-response function shape

    -   lin_lin = linear-linear ERF shape
    -   log_lin = log-linear ERF shape
    -   function = case where the ERF is defined by multiple points (x and y coordinates), e.g. the MR-BRT curves from GBD
    -   formula = case where ERF is a formula of the type a * x + b * x^2 ...

-   *exp* specifies the type of exposure input data

    -   single = single exposure input value, e.g. yearly average population-weighted PM2.5 exposure
    -   dist = exposure distribution, e.g. 5 different exposure categories (\~ exposure ranges) with the information how many people are exposed to each of the 5 exposure range

-   *iteration* specifies whether the assessment is done for more than one geo unit (e.g. municipality, region, province, ...)

    -   if yes –\> TRUE
    -   if no –\> FALSE

### Basic function template

```{r template rr complete basic, include=TRUE, echo=TRUE, eval=FALSE}
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

## healthiar FUNCTION CALL
healthiar::attribute_health(
  approach_risk = "relative_risk",
  erf_shape = ,
  rr_central = ,
  rr_lower = NULL, 
  rr_upper = NULL,
  rr_increment = ,
  exp_central = ,
  exp_lower = NULL, 
  exp_upper = NULL,
  cutoff_central = ,
  cutoff_lower = NULL, 
  cutoff_upper = NULL,
  bhd_central = ,
  bhd_lower = NULL, 
  bhd_upper = NULL,
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
)
    
## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template rr complete extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::attribute_health(
        approach_risk = "relative_risk",
        erf_shape = ,
        rr_central = ,
        rr_lower = NULL, 
        rr_upper = NULL,
        rr_increment = ,
        exp_central = ,
        exp_lower = NULL, 
        exp_upper = NULL,
        cutoff_central = ,
        cutoff_lower = NULL, 
        cutoff_upper = NULL,
        bhd_central = ,
        bhd_lower = NULL, 
        bhd_upper = NULL,
        geo_id_disaggregated = NULL,
        geo_id_aggregated = NULL
      )$health_main$impact_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

## Absolute risk pathways

Depending on your calculation pathway you will have to replace some of the `NULL` values in the template.

### Explanation of pathway ID

The pathway ID for absolute risk pathways contain the following elements:

-   *erf* contains the exposure-response function shape

    -   function = case where the ERF is defined by multiple points (x and y coordinates), e.g. the MR-BRT curves from GBD
    -   formula = case where ERF is a formula of the type a * x + b * x^2 ...

-   *exp* specifies the type of exposure input data

    -   single = single exposure input value, e.g. yearly average population-weighted PM2.5 exposure
    -   dist = exposure distribution, e.g. 5 different exposure categories (\~ exposure ranges) with the information how many people are exposed to each of the 5 exposure range

-   *iteration* specifies whether the assessment is done for more than one geo unit (e.g. municipality, region, province, ...)

    -   if yes –\> TRUE
    -   if no –\> FALSE

### Basic function template

```{r template ar complete basic, include=TRUE, echo=TRUE, eval=FALSE}
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

healthiar::attribute_health(
  approach_risk = "absolute_risk",
  erf_eq_central = ,
  erf_eq_lower = NULL,
  erf_eq_upper = NULL,
  exp_central = ,
  exp_lower = NULL, 
  exp_upper = NULL,
  pop_exp = ,
  geo_id_disaggregated = NULL,
  geo_id_aggregated = NULL
)

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template ar complete extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::attribute_health(
        approach_risk = "absolute_risk",
        erf_eq_central = ,
        erf_eq_lower = NULL,
        erf_eq_upper = NULL,
        exp_central = ,
        exp_lower = NULL, 
        exp_upper = NULL,
        pop_exp = ,
        geo_id_disaggregated = NULL,
        geo_id_aggregated = NULL
      )$health_main$impact_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

## Monetization pathways

See start of the section [Testing templates] for guidance on how to access function-specific info about the `include_monetization` function.

Depending on your calculation pathway you will have to replace some of the `NULL` values in the template.

### Explanation of pathway ID

The pathway ID for monetization pathways contain the following elements:

-   *discount_rate* specifies whether discounting for future years is done

    -   if yes –\> TRUE
    -   if no –\> FALSE
    
-   *discount_shape* specifies the formula shape to be used for discounting

    -   exponential = exponential discount equation
    -   hyp_harvey = hyperbolic discount equation based on the work of Harvey (1986)
    -   hyp_mazur = hyperbolic discount equation based on the work of Mazur (1986)

-   *inflation* specifies whether annual inflation (increase of prices) is applied

    -   if yes –\> TRUE
    -   if no –\> FALSE

### Basic function template

```{r template monetization complete basic, include=TRUE, echo=TRUE, eval=FALSE}
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

## healthiar FUNCTION CALL
healthiar::monetize(
  output_healthiar = NULL, # Only specify one of either "output_healthiar" or "impact" argument 
  impact = , # Only specify one of either "output_healthiar" or "impact" argument 
  valuation = ,
  cost = ,
  discount_rate = NULL,
  discount_shape = NULL,
  discount_years = 1,
  inflation = NULL
)

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template monetization complete extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::monetize(
        output_healthiar = NULL, # Only specify one of either "output_healthiar" or "impact" argument 
        impact = , # Only specify one of either "output_healthiar" or "impact" argument 
        valuation = ,
        cost = ,
        discount_rate = NULL,
        discount_shape = NULL,
        discount_years = 1,
        inflation = NULL
        )$monetization_main$monetized_impact,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

## Cost-benefit analysis pathways

Depending on your calculation pathway you will have to replace some of the `NULL` values in the template.

### Basic function template

```{r template cba complete basic, include=TRUE, echo=TRUE, eval=FALSE}

  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

    ## healthiar FUNCTION CALL
    object =
      healthiar::cba(
        output_healthiar = NULL,
        positive_impact = ,
        valuation = ,
        cost = ,
        discount_shape = ,
        discount_rate_benefit = ,
        discount_rate_cost = ,
        discount_years_benefit = 1,
        discount_years_cost = 1) 

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template cba complete extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::cba(
        output_healthiar = NULL,
        positive_impact = ,
        valuation = ,
        cost = ,
        discount_shape = ,
        discount_rate_benefit = ,
        discount_rate_cost = ,
        discount_years_benefit = 1,
        discount_years_cost = 1)$cba_main$net_benefit_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

## Iteration

The iteration function calls require two additional arguments compared to the function calls for single geo units: you have to additionally specify the `geo_id_disaggregated` (e.g. "Brussels", "Antwerp", ...) and `geo_id_aggregated` (e.g. "Belgium") arguments. Also, the geo unit-specific arguments (e.g. `exp_central`, `bhd_central`, ...) have to be provided as lists, with each list element representing a geo unit. For more detailed information on iterations using `attribute_...` functions please see section *Example iteration: assess impact in multiple geographic units* in the *intro_to_healthiar* vignette.

### Basic function template

```{r template iteration rr basic, include=TRUE, echo=TRUE, eval=FALSE}
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

    ## healthiar FUNCTION CALL
      healthiar::attribute_health(
        approach_risk = "relative_risk",
        erf_shape = , # Note: numeric vector must be wrapped by as.list() fct
        rr_central = ,
        rr_lower = NULL, 
        rr_upper = NULL,
        rr_increment = ,
        exp_central = , # Note: numeric vector must be wrapped by as.list() fct
        exp_lower = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        exp_upper = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        cutoff_central = ,
        cutoff_lower = NULL, 
        cutoff_upper = NULL,
        bhd_central = , # Note: numeric vector must be wrapped by as.list() fct
        bhd_lower = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        bhd_upper = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        geo_id_disaggregated = ,
        geo_id_aggregated = 
      )

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template iteration rr extended, include=TRUE, echo=TRUE, eval=FALSE}
testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
      healthiar::attribute_health(
        approach_risk = "relative_risk",
        erf_shape = , # Note: numeric vector must be wrapped by as.list() fct
        rr_central = ,
        rr_lower = NULL, 
        rr_upper = NULL,
        rr_increment = ,
        exp_central = , # Note: numeric vector must be wrapped by as.list() fct
        exp_lower = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        exp_upper = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        cutoff_central = ,
        cutoff_lower = NULL, 
        cutoff_upper = NULL,
        bhd_central = , # Note: numeric vector must be wrapped by as.list() fct
        bhd_lower = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        bhd_upper = NULL, # Note: if numeric vector entered it must be wrapped by as.list() fct
        geo_id_disaggregated = ,
        geo_id_aggregated = 
      )$health_main$impact_rounded,
    ##  RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

## Social analysis

Note that to test the `socialize` function you a social indicator for each of the geo units under analysis in addition to the usual data needed for an iteration of `attribute`.

### Basic function template

```{r template social analysis basic, include=TRUE, echo=TRUE, eval=FALSE}
## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
# data <- ...

## First run an iteration (see iteration template for full argument list)
result_interim <- healthiar::attribute_health(
  exp_central = as.list( ),
  bhd_central = as.list( ),
  cutoff_central = ,
  rr_central = , 
  erf_shape = , 
  rr_increment = ,
  geo_id_disaggregated = 
)

## healthiar FUNCTION CALL
healthiar::socialize(
  output_healthiar = result_interim,
  geo_id_disaggregated = , # geo IDs of the preparatory iteration call above and this function call must match!
  social_indicator = ,
  n_quantile = , # Specify number of quantiles, e.g. 10
  approach = "quantile" # default (and currently only) approach
)

## RESULT(S) COMPARISON ASSESSMENT:
## List here the results of the comparison assessment you selected
## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```

### Extended function template

```{r template social analysis extended, include=TRUE, echo=TRUE, eval=FALSE}

testthat::test_that("results correct [pathway_id]", {
  
  ## IF APPLICABLE: LOAD INPUT DATA BEFORE RUNNING THE FUNCTION
  # data <- ...
  
  ## First run an iteration (see iteration template for full argument list)
  result_interim <- healthiar::attribute_health(
    exp_central = as.list( ),
    bhd_central = as.list( ),
    cutoff_central = ,
    rr_central = , 
    erf_shape = , 
    rr_increment = ,
    geo_id_disaggregated = 
  )

  testthat::expect_equal(
    ## healthiar FUNCTION CALL
    object =
        healthiar::socialize(
          output_healthiar = result_interim,
          geo_id_disaggregated = , # geo IDs of the preparatory iteration call above and this function call must match!
          social_indicator = ,
          n_quantile = , # Specify number of quantiles, e.g. 10
          approach = "quantile" # default (and currently only) approach
        ) |>
      purrr::pluck("social_main") |> 
      dplyr::filter(
        difference_type == "absolute" & 
          difference_compared_with == "overall")  |>
      dplyr::select(difference_value) |> 
      base::unlist() |>
      base::as.numeric(),
    
    ## RESULT(S) FROM THE COMPARISON ASSESSMENT YOU SELECTED
    expected =
      c( )
    )
})

## ASSESSOR:
## Add here your name and your institute abbreviation
## ASSESSMENT DETAILS: 
## Add here short description of the assessment: year, metric (e.g. DALY, premature deaths, ...), ...
## INPUT DATA DETAILS: 
## Add here input data details: data sources, measured vs. modelled, ...
```
